How to improve your relationship with your future self.

### 2016-05-20 workflow.Rmd
Starting to transition to Rmd

\documentclass[12pt]{article}
\usepackage{fancyvrb,natbib,url,array,dcolumn,float,booktabs,listings}
\usepackage[colorlinks=TRUE]{hyperref}
\usepackage{microtype}

\title{Six steps to a better relationship with your future self.}

\author{Jake Bowers\thanks{I owe many thanks to Mark Fredrickson,
    Brian Gaines, Kieran Healy, Kevin Quinn and Cara
    Wong for direct help on this document and to Mika LaVaque-Manty
    and Ben Hansen for many useful discussions on this topic. The
    source code for this document may be freely downloaded and
    modified from \url{https://github.com/jwbowers/workflow}.}}

\date{\today}

\newcolumntype{.}{D{.}{.}{1.2}}

\usepackage[noae,nogin]{Sweave} %Declaring this explicitly so that I can modify the Sweave environment here rather in Sweave.sty which will be c
\DefineVerbatimEnvironment{Sinput}{Verbatim} {xleftmargin=.5em,fontsize=\footnotesize}
\DefineVerbatimEnvironment{Soutput}{Verbatim}{xleftmargin=.5em,fontsize=\footnotesize}
\DefineVerbatimEnvironment{Scode}{Verbatim}  {xleftmargin=.5em,fontsize=\footnotesize}
\fvset{listparameters={\setlength{\topsep}{0pt}}}
\renewenvironment{Schunk}{\vspace{\topsep}}{\vspace{\topsep}}
\SweaveOpts{keep.source=TRUE}  %Show comments
\fvset{fontsize=\footnotesize} %slightly smaller verbatim font

%% These next lines tell latex that it is ok to have a single graphic
%% taking up most of a page, and they also decrease the space arou
%% figures and tables.
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.1}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}
\setlength{\intextsep}{2ex}
\setlength{\floatsep}{2ex}
\setlength{\textfloatsep}{2ex}

\begin{document}
\frenchspacing
\VerbatimFootnotes
\maketitle

<<initialize,echo=FALSE,results=hide>>=
  ##First, just setup the \R environment:
  options(SweaveHooks=list(
            fig=function(){
              par(mar=c(3.5, 3, 1.1, 0),
                  pty="s",
                  mgp=c(1.5,0.5,0),
                  oma=c(0,0,0,0))},#,
            echo=function(){options(continue=" ") ##Don't show "+" prompts,
                            options(prompt=" ")}
            ),
          digits=3,
          scipen=8,
          width=50,
          error=function(){options(prompt="> ",continue="+ ");NULL}
          )

@

@@

%%% This data frame will be used throughout the analyses.
%%% Putting it up top, so we can use it in the comments section.
<<read.data,echo=FALSE,results=hide>>=
##  This read.csv line is slightly more complex than needed because of
##  the particular encoding used for characters in the source file.
dem.nations.df<-read.csv(url("http://www.hks.harvard.edu/fs/pnorris/Data/Democracy%20CrossNational%20Data/Democracy%20Crossnational%20Data%20Spring%202009.csv",encoding="ISO_8859-1"),as.is=TRUE)
row.names(dem.nations.df)<-dem.nations.df$Natabrv ##make the row names more helpful
good.df<-na.omit(dem.nations.df[,c("Gini2004","protac2000","Nation","meanpr")])
good.df$gini04<-good.df$Gini2004/100
good.df$protac00<-good.df$protac2000
@

@@

% <<reg1,echo=TRUE,results=verb>>=
% ##  Repeat the regression run for Table~\ref{tab:protest}
% ##  Do political rights predict protest reporting?
% lm1 <- lm(protac00 ~ gini04 + meanpr, data=good.df)
% ##  Q: Was it worthwhile controlling for political rights?
% lm2 <- lm(protac00~gini04,data=good.df)
% coef(lm2)[2]-coef(lm1)[2]
% ##  A: Yes (around 3/4 an act of protest difference)
% @

@@

\begin{Verbatim}[fontsize=\footnotesize]
This paper, for example, was written in plain text using \LaTeX
markup with R code chunks to make things like
Figure~\ref{fig:giniprot}. This combination of \LaTeX and R is
called Sweave \citep{Leis:2005}.\footnote{Support for Sweave is
  included with R.}
\begin{figure}[h]
\centering
 <<fig1plot,fig=TRUE>>=
 ##  Make a scatterplot of Protest by Inequality
 with(good.df,plot(gini04,protac00,xlab='Gini Coefficient 2004 (UNDP)',
                   ylab='Mean Protest Activities\n(World Values Survey 1980-2000)'))
 ##  Label a few interesting points
 with(good.df[c("EGY","JOR","USA","SWE","CHL"),],
      text(gini04,protac00,labels=Nation))
 @
\caption{Protest activity by income inequality \citep[from][]{norris2009data}.}
\label{fig:giniprot}
\end{figure}
\end{Verbatim}

<<fig1code,echo=FALSE,fig=FALSE>>=
##  Make a scatterplot of Protest by Inequality
with(good.df,plot(gini04,protac00,
                  xlab='Gini Coefficient 2004 (UNDP)',
                  ylab='Mean Protest Activities\n(World Values Survey 1980-2000)',
                  cex=.8))

##  Label a few interesting points
with(good.df[c("EGY","JOR","USA","SWE","CHL"),],
     text(gini04,protac00,labels=Nation,srt=0,cex=.6,pos=3,offset=.1))
@

\begin{figure}[H]
  \begin{center}
<<fig1plot,echo=FALSE,fig=TRUE,width=4,height=4>>=
par(bty="n",xpd=TRUE,pty="s",tcl=-.25)
<<fig1code>>
@
    \caption{Protest activity by income inequality \citep[from][]{norris2009data}.}
    \label{fig:giniprot}
  \end{center}
\end{figure}

@@

<<maketable, echo=FALSE, results=hide>>=
  lm1<-lm(protac00~gini04+meanpr,data=good.df)  #  Run the regression

@@

library(xtable)
thextab<-xtable(themat,align=c("l",rep(".",4)),digits=1,
                caption="People living in countries with unequal
  income distributions report less protest activity to World Values
  Survey interviewers than people living in countries with relatively
  more equal income distributions, adjusting for average political
  rights as measured by Freedom House 1980--2000. Data from \\citep{norris2009data}.",label="tab:protest")
@

<<printtable,echo=FALSE,results=tex>>=
  print(thextab,include.colnames=FALSE,
        hline.after=NULL,
        table.placement="H",
        add.to.row=list(
          pos=list(0,3),
          command=c(
            "\\toprule \n &
             \\multicolumn{1}{c}{Coef} &
             \\multicolumn{1}{c}{Std. Err.} &
             \\multicolumn{2}{c}{95\\% CI} \\\\ \\cmidrule(r){2-5} ",
            paste("& \\multicolumn{4}{c}{n: ",n,",",
                  "   resid.sd: ",signif(est.sigma),
                  ", R$^2$: ",r2,"} \\\\ \\bottomrule",sep="")
            )
          ))
@

@@

<<unit.test>>=
##  The test function:
test.times.2.fn <- function(){
  ##  This function tests times.2.fn
  if (times.2.fn(thenumber=4) ==  8 &
      times.2.fn(thenumber=-4) == -8) { 
    print("It works!")
  } else { print("It does not work!")
         }
}

@@

##  Use the test function
test.times.2.fn()
@

@@

\end{document}
<<>>=
options(prompt="> ",continue="+ ")
@

>>>>

---
title: How to improve your relationship with your future self.
author: 
- name: Jake Bowers\thanks{I owe many thanks to Mark Fredrickson,
    Brian Gaines, Kieran Healy, Kevin Quinn and Cara
    Wong for direct help on this document and to Mika LaVaque-Manty
    and Ben Hansen for many useful discussions on this topic. The
    source code for this document may be freely downloaded and
    modified from \url{https://github.com/jwbowers/workflow}.}
  affiliation: <jwbowers@illinois.edu>, University of Illinois at Urbana-Champaign and White House Social and Behavioral Sciences Team
- name: Maarten Voors
  affiliation: Wageningen University
date: 20 May 2016
...

```{r initialize,echo=FALSE,results=hide}
  ##First, just setup the \R environment:
  options(SweaveHooks=list(
            fig=function(){
              par(mar=c(3.5, 3, 1.1, 0),
                  pty="s",
                  mgp=c(1.5,0.5,0),
                  oma=c(0,0,0,0))},#,
            echo=function(){options(continue=" ") ##Don't show "+" prompts,
                            options(prompt=" ")}
            ),
          digits=3,
          scipen=8,
          width=50,
          error=function(){options(prompt="> ",continue="+ ");NULL}
          )

```

@@

%%% This data frame will be used throughout the analyses.
%%% Putting it up top, so we can use it in the comments section.
```{r read.data,echo=FALSE,results=hide}
##  This read.csv line is slightly more complex than needed because of
##  the particular encoding used for characters in the source file.
dem.nations.df<-read.csv(url("http://www.hks.harvard.edu/fs/pnorris/Data/Democracy%20CrossNational%20Data/Democracy%20Crossnational%20Data%20Spring%202009.csv",encoding="ISO_8859-1"),as.is=TRUE)
row.names(dem.nations.df)<-dem.nations.df$Natabrv ##make the row names more helpful
good.df<-na.omit(dem.nations.df[,c("Gini2004","protac2000","Nation","meanpr")])
good.df$gini04<-good.df$Gini2004/100
good.df$protac00<-good.df$protac2000
```

@@

% ```{r reg1,echo=TRUE,results=verb}
% ##  Repeat the regression run for Table~\ref{tab:protest}
% ##  Do political rights predict protest reporting?
% lm1 <- lm(protac00 ~ gini04 + meanpr, data=good.df)
% ##  Q: Was it worthwhile controlling for political rights?
% lm2 <- lm(protac00~gini04,data=good.df)
% coef(lm2)[2]-coef(lm1)[2]
% ##  A: Yes (around 3/4 an act of protest difference)
% ```

@@

\begin{Verbatim}[fontsize=\footnotesize]
This paper, for example, was written in plain text using \LaTeX
markup with R code chunks to make things like
Figure~\ref{fig:giniprot}. This combination of \LaTeX and R is
called Sweave \citep{Leis:2005}.\footnote{Support for Sweave is
  included with R.}
\begin{figure}[h]
\centering
 ```{r fig1plot,fig=TRUE}
 ##  Make a scatterplot of Protest by Inequality
 with(good.df,plot(gini04,protac00,xlab='Gini Coefficient 2004 (UNDP)',
                   ylab='Mean Protest Activities\n(World Values Survey 1980-2000)'))
 ##  Label a few interesting points
 with(good.df[c("EGY","JOR","USA","SWE","CHL"),],
      text(gini04,protac00,labels=Nation))
 ```
\caption{Protest activity by income inequality \citep[from][]{norris2009data}.}
\label{fig:giniprot}
\end{figure}
\end{Verbatim}

```{r fig1code,echo=FALSE,fig=FALSE}
##  Make a scatterplot of Protest by Inequality
with(good.df,plot(gini04,protac00,
                  xlab='Gini Coefficient 2004 (UNDP)',
                  ylab='Mean Protest Activities\n(World Values Survey 1980-2000)',
                  cex=.8))

##  Label a few interesting points
with(good.df[c("EGY","JOR","USA","SWE","CHL"),],
     text(gini04,protac00,labels=Nation,srt=0,cex=.6,pos=3,offset=.1))
```

\begin{figure}[H]
  \begin{center}
```{r fig1plot,echo=FALSE,fig=TRUE,width=4,height=4}
par(bty="n",xpd=TRUE,pty="s",tcl=-.25)
```{r fig1code>>
```
    \caption{Protest activity by income inequality \citep[from][]{norris2009data}.}
    \label{fig:giniprot}
  \end{center}
\end{figure}

@@

```{r maketable, echo=FALSE, results=hide}
  lm1<-lm(protac00~gini04+meanpr,data=good.df)  #  Run the regression

@@

library(xtable)
thextab<-xtable(themat,align=c("l",rep(".",4)),digits=1,
                caption="People living in countries with unequal
  income distributions report less protest activity to World Values
  Survey interviewers than people living in countries with relatively
  more equal income distributions, adjusting for average political
  rights as measured by Freedom House 1980--2000. Data from \\citep{norris2009data}.",label="tab:protest")
```

```{r printtable,echo=FALSE,results=tex}
  print(thextab,include.colnames=FALSE,
        hline.after=NULL,
        table.placement="H",
        add.to.row=list(
          pos=list(0,3),
          command=c(
            "\\toprule \n &
             \\multicolumn{1}{c}{Coef} &
             \\multicolumn{1}{c}{Std. Err.} &
             \\multicolumn{2}{c}{95\\% CI} \\\\ \\cmidrule(r){2-5} ",
            paste("& \\multicolumn{4}{c}{n: ",n,",",
                  "   resid.sd: ",signif(est.sigma),
                  ", R$^2$: ",r2,"} \\\\ \\bottomrule",sep="")
            )
          ))
```

@@

```{r unit.test}
##  The test function:
test.times.2.fn <- function(){
  ##  This function tests times.2.fn
  if (times.2.fn(thenumber=4) ==  8 &
      times.2.fn(thenumber=-4) == -8) { 
    print("It works!")
  } else { print("It does not work!")
         }
}

@@

##  Use the test function
test.times.2.fn()
```

@@

\end{document}
```{r }
options(prompt="> ",continue="+ ")
```
